Title

### 2024-05-07 paper/main.tex
Updates

\begin{enumerate}
	\item Algorithsm can be biased towards sparse graphs. Ref: Malinsky's paper.
	\item Algorithms making obvious mistakes: These algorithms often 
		make very obvious mistakes, making it harder for the user
		to trust them.
	\item Difficulties in choosing an algorithm: For any given dataset, the
		user need to make a choice of the algorithm. Given that these
		algorithms work very differently, it can be difficult to make a
		choice. Additionally, each of these algorithms have
		hyperparameters and choices to make for them, making it
		difficult. As there is no way to evaluate the performance of 
		these algorithms on our dataset.
\end{enumerate}

@@

\begin{figure}
		\centering
		\begin{tikzpicture}
			\begin{scope}[yshift=0.7cm, scale=0.8]
			\tikzstyle{every node}=[align=center, inner sep=1pt]
				\node (sex) at (-0.7, -0.8) {Sex};
				\node (age) at (-0.3, 0) {Age};
				\node (ed) at (-1.8, -1.6) {Education};
				\node (occ) at (1.8, 0) {Occupation};
				\node (hrpw) at (1.3, -1.6) {Hours Per \\ Week};
				\node (income) at (-0.7, -2.8) {Income};

@@

\section{Background}
\todo[inline]{Add notation used here}

We need to do both conditional and non-conditional tests. We would assume that
we are testing the statement $ X \ci Y \rvert \bm{Z} $, where $ \bm{Z} $ is a
set of conditional variables possibly null.

@@

\subsubsection{Continuous Variables}
In the case when $ \bm{Z} = \emptyset $, and when both $ X $ and $ Y $ are
continuous variables, Pearson's correlation coefficient based test can be used
which also gives an effect size measure. The p-value computation requires the
data to be normally distributed but other statistics can be used such as
Spearman's rank correlation, or Kendall's Tau.

@@

\subsubsection{Discrete Variables}

@@

When $ \bm{Z} \neq \emptyset $, we do stratification.

\subsubsection{Ordinal and Continuous Variables}
Polyserial Correlation

@@

\subsubsection{Ordinal Variables}
Polychoric Correlation

>>>>

\begin{enumerate}
	\item Biased towards sparse graphs.
	\item Algorithms making obvious mistakes: These algorithms often 
		make very obvious mistakes, making it harder for the user
		to trust them.
	\item Difficulties in choosing an algorithm: For any given dataset, the
		user need to make a choice of the algorithm. Given that these
		algorithms work very differently, it can be difficult to make a
		choice. Additionally, each of these algorithms have
		hyperparameters and choices to make for them, making it
		difficult. As there is no way to evaluate the performance of 
		these algorithms on our dataset.
\end{enumerate}

@@

\begin{figure}
		\centering
		\begin{tikzpicture}
			\begin{scope}[yshift=0.7cm, scale=1]
			\tikzstyle{every node}=[align=center, inner sep=1pt]
				\node (sex) at (-0.7, -0.8) {Sex};
				\node (age) at (-0.3, 0) {Age};
				\node (ed) at (-1.8, -1.6) {Education};
				\node (occ) at (1.8, 0) {Occupation};
				\node (hrpw) at (1.3, -1.6) {Hours Per \\ Week};
				\node (income) at (-0.7, -2.8) {Income};

@@

\section{Background}
We consider one-dimensional variables $ X $, and $ Y $ and a possibly
multi-dimensional co$ Z = Z_1, \cdots, Z_k $, potentially being an empty set $
Z = \emptyset $. We consider various scenarios where the variables $ X $, $ Y $
and $ Z $ could be either discrete, ordinal, or continuous. With mixed data, we
mean an arbitrary mix of variable types among $ X $, $ Y $, and $ Z $.

We consider the problem of estimating the partial (or conditional) association
between $ X $ and $ Y $ in the presence of the conditioning set $ Z $. When $ Z
= \emptyset $, this is equivalent to the marginal association between $ X $ and
$ Y $.

\todo[inline]{Add more notation as they come}

@@

\subsubsection{$ X $ and $ Y $ are continuous}
In the case when $ \bm{Z} = \emptyset $, and when both $ X $ and $ Y $ are
continuous variables, Pearson's correlation coefficient based test can be used
which also gives an effect size measure. The p-value computation requires the
data to be normally distributed but other statistics can be used such as
Spearman's rank correlation, or Kendall's Tau.

@@

\subsubsection{All $ X $, $ Y $, $ Z $ are discrete}

@@

When $ \bm{Z} \neq \emptyset $, we can do stratification.

\subsubsection{$ X $ is ordinal and $ Y $ is continuous}
Polyserial Correlation

@@

\subsubsection{$ X $ and $ Y $ are ordinal}
Polychoric Correlation
